A Microservices Based Approach for City Traffic Simulation

### 2020-02-20 papers/traffic simulation/paper.tex
Fixed paper.tex

The paper proposes a city traffic software simulation based on actors which run independently of one another and have specific characters in their behavior. To run indepentently actors are modeled as microservices and they are running within an orchestration framework. Their specific behavior is modeled as simple algorithms, embedded in each actor's type code. They may act based on the data about all the other actors, data which is gathered together by a single entity called city simulator. An orchestration model is proposed and all the actors have a communication protocol to offer data to the city simulator and request data from it.

@@

In \cite{8569576} the broad idea is to use a discrete event architecture, in which there are logical processes for executing and simulating a number of agents. For a computation intensive aim those processes can be clustered into agent clusters with dependencies between them, but the paper avoids presenting the necessary details on how it would work. The particularity of this proposal is that it crosses the boundaries of a single computing machine and pave a way to distribute the load and information across machines, with certain limitations and challenges.

An approach which is focused on junction modeling is \cite{urban-traffic-sim}. As opposed to the generality of various other related works, \cite{urban-traffic-sim} is focused on two specific and real junctions. The simulation stems from SUMO, using real data acquired from cameras placed in junctions (and analyzed with image processing technologies) and is relaying traffic data to a Matlab instance. The simulation is aiming at evaluating metrics of the traffic which flows through junctions: arrival flow and queue length. This idea is closely related to an enhancement proposed in section \ref{sec:enhancements}.

@@

Microservices concept has been presented and together with it the city simulator and the city actor types have been introduced. Their interactions, through a specific protocol, have been presented. Moreover, various other interactions, with supporting roles (routing engine and web page) have been presented: the routing engine can be called by any actor via a REST based API and the web page keeps an open WebSocket connection towards the city simulator to be notified of any change. Design choices, lead by the programming language (Go language) and container tool (Docker) have been discussed, together with their advantages. Networking details and design have been detailed, mostly lead by how the Docker and linux containers landscape works. Kubernetes, as the de facto solution for microservices orchestration was also presented. Finally, a brief description provided the results of a simulation run on a single machine.

>>>>

The paper proposes a city traffic software simulation based on actors which run independently of one another and have specific characters in their behavior. To run indepentently actors are modeled as microservices and they are running within an orchestration framework. Their behavior is modeled as with specific algorithms for each of their type, embedded in each actor's type code. They may act based on the data about all the other actors, data which is gathered together by a single entity called city simulator. An orchestration model is proposed and all the actors use a communication protocol to offer data to the city simulator and request data from it.

@@

In \cite{8569576} the broad idea is to use a discrete event architecture, in which there are logical processes for executing and simulating a number of agents. For a computation intensive aim those processes can be clustered into agent clusters with dependencies between them, but the paper avoids presenting the necessary details on how the distributed mechanics would work. The particularity of this proposal is that it crosses the boundaries of a single computing machine and pave a way to distribute the load and information across machines, with certain limitations and challenges.

An approach which is focused on junction modeling is \cite{urban-traffic-sim}. As opposed to the generality of various other related works, \cite{urban-traffic-sim} is focused on two specific and real junctions. The simulation stems from SUMO, using real data acquired from cameras placed in junctions (and analyzed with image processing technologies) and is relaying traffic data to a Matlab instance. The simulation is aiming at evaluating metrics of the traffic which flows through junctions: arrival flow and queue length. This idea is closely related to an enhancement proposed in section \ref{sec:enhancements} around junction modeling.

@@

Microservices concept has been presented and together with it the city simulator and the city actor types have been introduced. Their interactions, through a specific protocol, have been presented. Moreover, various other interactions, with supporting roles (routing engine and web page) have been presented: the routing engine can be called by any actor via a REST based API and the web page keeps an open WebSocket connection towards the city simulator to be notified of any change. Design choices, lead by the programming language (Go language) and container tool (Docker) have been discussed, together with their advantages. Networking details and design have been detailed, mostly lead by how the Docker and Linux containers landscape work. Kubernetes, as the de facto solution for microservices orchestration was also presented. Finally, a brief description provided the results of a simulation run on a single machine.
